---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# rzentra

<!-- badges: start -->
[![Lifecycle: maturing](https://img.shields.io/badge/lifecycle-maturing-blue.svg)](https://www.tidyverse.org/lifecycle/#maturing)
[![CRAN status](https://www.r-pkg.org/badges/version/rzentra)](https://CRAN.R-project.org/package=rzentra)
[![R build status](https://github.com/basf/rzentra/workflows/R-CMD-check/badge.svg)](https://github.com/basf/rzentra/actions)
[![codecov](https://codecov.io/gh/basf/rzentra/branch/master/graph/badge.svg?token=DJ6PVJQLRZ)](https://codecov.io/gh/basf/rzentra)
<!-- badges: end -->

An R client for [Zentracloud API](https://zentracloud.com/api/v1/guide#APIGuidelines).

## Installation


## Example

```{r load}
library("rzentra")
```

### Authentcation

To work with the API you first need to authenticate.
The `zc_token()` function authenticates you with your username and password and returns a `token` that can be used in subsequent API-calls.

The `username` & `password` are by default read from environmental variables
`ZC_USERNAME` and `ZC_PASSWORD`, but you can provide them also in every function call
using the `username=` and `password=` arguments.


```{r token, eval=FALSE}
token <- zc_token(username = "yourname", password = "yourpassword")$token
```



### Querying data

#### Device settings

Querying the settings of a device can be done with `zc_settings`

```{r settings, eval=FALSE}
zc_settings(token = token, 
  sn = "z6-00033", 
  start_time = as.numeric(as.POSIXct(Sys.Date(), origin = "1970-01-01"))
  )
```

#### Device statuses

Querying the settings of a device can be done with `zc_statuses`

```{r status, eval=FALSE}
zc_statuses(token = token, 
  sn = "z6-00033", 
  start_time = as.numeric(as.POSIXct(Sys.Date(), origin = "1970-01-01"))
  )
```

#### Device readings

```{r readings, eval=FALSE}
zc_readings(token = token, 
  sn = "z6-00033", 
  start_time = as.numeric(as.POSIXct(Sys.Date(), origin = "1970-01-01"))
  )
```
### Parsing data

Readings can be parsed into a long time-series table with `zc_timeseries()`

```{r parse, eval=FALSE}
head(
  zc_timeseries(readings)
)
```


